\bfseries The spherical scow:\\ A simple model for sailing

### 2025-01-25 paper/main.tex
various things

% to-do items:
% ------------
% - Update figure captions to match new figures!
% - Add to the abstract and the introduction and discussion that this is only a 2-D model of sailing. Not 3-D!
% - Add to the abstract the point that the sailboat is defined by 3 dimensionless numbers: The sail-to-keel ratio, and two lift ratios.
% - Change citations to Tao to make it clear that the Tao model is (probably) wrong!!
% - Make sure I cite {symmetry} appropriately in various places. Probably also point out that it is a fun longer read.
% - Make sure we aren't claiming that the model is NOVEL. It is just SIMPLE.
% - Reconsider the post-equation commas? (HWR SAY).
% — Make some comments on the situations in which the ram-pressure force approximation is more appropriate---gale force or lull?
% - Is the latex footnote-footnote separation fucked?
% - Do we still mention "tensors" anywhere? make sure the abstract is consistent with the body.
% - Respond to comments by Hyung Don Ryoo, in email to Hogg, 2021-07-15.
% - Make sure the spirit of the bibliographic comments get pulled into the main text (and removed from the bibiliography).
% - Fix the et al typography in the bibliography?
% - Are we clear that we also find that you can sail faster than the wind, in general, like cross-wind? Emphasize that when we first figure it out.
% - What claims in the literature exist about maximum boat speeds? Have I seen a 2x wind claim? We can beat that. Have I seen a "never faster downwind than the wind" (as in Kimball) or than 0.5 times the wind claim? We can perhaps beat that too.
% - Should we be more careful to use Galilean-relativistic language, like instead of "upwind" say "upwind relative to the water"? Like always?
% - Mention sailing hydrofoil where we discuss the keel lift ratio: The point of the hyrdrofoil is to reduce A_below.
% - Explain why amateur sailboats have huge keels and professional boats have small keels. Upwind sailing is the answer!
% - Kleban points about non-trivial wind force f(theta) and references (in email, maybe).
% - Note that better sailing (tm) is almost never in the direction of the target!
% - Is there an analog of the Betts or Betz limit? Also just generally discussion of power, power dissipated, and so on.
% - Do we adequately mention sustainability in the introduction?
% - How to plot the phase space of dimensionless ratios that allow for UW and DWFTTW?
% - Can we address stability and uniqueness of the solutions to the (quartic, actually) equations?
% - Do we clearly define the dimensionless ratios that define a boat? There are three.
% - Kleban wants polars -- plots that are used in the business. Can do!
% - Discuss "velocity made good" in the text and maybe name-check it in the abstract?
% -

@@

\title{\bfseries%
The spherical scow: a simple model for sailboats}
\markright{\textsf{Hogg \& Kleban / A momentum-transport model for sailing}}
\author{DWH, MK, others?}
\date{2021--2024}
\begin{document}
\maketitle

@@

\paragraph{Acknowledgements:}
It is a pleasure to thank
  Lehman Garrison (Flatiron),
  Will Kinney (Buffalo),
  Hans-Walter Rix (MPIA),
  Hyung-Don Ryoo (NYU), and
  Soledad Villar (JHU)
for valuable discussions and comments.
All code used to solve equations and make figures in this \documentname{} is available under the open-source \textsl{MIT License} at \url{https://github.com/davidwhogg/Sailing}.

>>>>

% to-do items:
% ------------
% - Incorporate references and terminology from Leif Ristroph (NYU). See email of 2025-01-24 and 25.
% - Update figure captions to match new figures!
% - Add to the abstract and the introduction and discussion that this is only a 2-D model of sailing. Not 3-D!
% - Add to the abstract the point that the sailboat is defined by 3 dimensionless numbers: The sail-to-keel ratio, and two lift ratios.
% - Change citations to Tao to make it clear that the Tao model is (probably) wrong!!
% - Make sure I cite {symmetry} appropriately in various places. Probably also point out that it is a fun longer read.
% - Make sure we aren't claiming that the model is NOVEL. It is just SIMPLE.
% - Reconsider the post-equation commas? (HWR SAY).
% — Make some comments on the situations in which the ram-pressure force approximation is more appropriate---gale force or lull?
% - Is the latex footnote-footnote separation fucked?
% - Do we still mention "tensors" anywhere? make sure the abstract is consistent with the body.
% - Respond to comments by Hyung Don Ryoo, in email to Hogg, 2021-07-15.
% - Make sure the spirit of the bibliographic comments get pulled into the main text (and removed from the bibiliography).
% - Fix the et al typography in the bibliography?
% - Are we clear that we also find that you can sail faster than the wind, in general, like cross-wind? Emphasize that when we first figure it out.
% - What claims in the literature exist about maximum boat speeds? Have I seen a 2x wind claim? We can beat that. Have I seen a "never faster downwind than the wind" (as in Kimball) or than 0.5 times the wind claim? We can perhaps beat that too.
% - Should we be more careful to use Galilean-relativistic language, like instead of "upwind" say "upwind relative to the water"? Like always?
% - Mention sailing hydrofoil where we discuss the keel lift ratio: The point of the hyrdrofoil is to reduce A_below.
% - Explain why amateur sailboats have huge keels and professional boats have small keels. Upwind sailing is the answer!
% - Kleban points about non-trivial wind force f(theta) and references (in email, maybe).
% - Note that better sailing (tm) is almost never in the direction of the target!
% - Is there an analog of the Betts or Betz limit? Also just generally discussion of power, power dissipated, and so on.
% - Do we adequately mention sustainability in the introduction?
% - How to plot the phase space of dimensionless ratios that allow for UW and DWFTTW?
% - Can we address stability and uniqueness of the solutions to the (quartic, actually) equations?
% - Do we clearly define the dimensionless ratios that define a boat? There are three.
% - Kleban wants polars -- plots that are used in the business. Can do!
% - Discuss "velocity made good" in the text and maybe name-check it in the abstract?
% -

@@

\title{\bfseries%
The spherical scow:\\
A simple model for sailing}
\markright{\textsf{Hogg \& Kleban / A momentum-transport model for sailing}}
\author{DWH, MK, others?}
\date{2021--2024}
\begin{document}
\maketitle

@@

\paragraph{Acknowledgements:}
It is a pleasure to thank
  Lehman Garrison (Flatiron),
  Will Kinney (Buffalo),
  Leif Ristroph (NYU),
  Hans-Walter Rix (MPIA),
  Hyung-Don Ryoo (NYU), and
  Soledad Villar (JHU)
for valuable discussions and comments.
All code used to solve equations and make figures in this \documentname{} is available under the open-source \textsl{MIT License} at \url{https://github.com/davidwhogg/Sailing}.
